% Auto-generated Data and Methods chapter. Facts are derived from files in reports/ and data/processed/.

\chapter{Data and Methods}

\label{ch:data_methods}

\section{Data sources}

The analysis uses processed data stored in the project's `data/processed` directory. Key processed files include `indexed_data.csv` and `clean_data.csv`. These contain company-level attributes, composite scores, and normalized factors used to build the index and run the experiments. The tables under `reports/tables` were produced by the analysis scripts and are referenced directly in the Results chapter.

For the standalone report package, local copies of the referenced tables and figures have been placed in the `Tables/` and `Figures/` directories at the root of this `Thesis_report` folder. These files are exact copies of the CSVs and PNGs produced by the analysis pipeline and are the factual sources for the Results chapter.

\\subsection{Software and data citation}

The analysis uses Python data libraries for processing and visualization; key tools include pandas, NumPy and Matplotlib which are cited here \cite{pandas_dev_2020, numpy, matplotlib}. Market and price data used to compute returns were obtained from public sources such as Yahoo Finance \cite{yahoo_finance}, and all derived tables included in this report are produced by the project's scripts and saved under `Tables/` and `Figures/`.

\section{Evaluation protocol}

Time-split evaluation uses train/holdout windows. Winners are selected using the latest available ranking within the training window and evaluated on holdout returns. The scripts produce summary CSVs and figures for each split; these outputs are included in the Results chapter. The evaluation code is in `scripts/07_time_split_evaluation.py`.

\section{Included tables}

The following processed tables from `reports/tables/` are included in the Results chapter:

\begin{itemize}

\item Time-split Evaluation -- source file: Tables/timesplit_evaluation_synthetic_summary.csv

\item Benchmark summary and portfolio performance -- source file: Tables/benchmark_summary.csv

\item Principal component analysis: explained variance -- source file: Tables/advanced_pca_variance.csv

\item Weight sensitivity and grid search -- source file: Tables/weight_grid_search.csv

\item Efficient frontier and optimal portfolios -- source file: Tables/advanced_efficient_frontier.csv

\end{itemize}