%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thesis / Project Report
% LaTeX Template
% Version 2.0 (08/04/16)
%
% Author:
% Siddhant Shrivastava
% https://github.com/sidcode/bits-pilani-thesis-template-latex
%
% License:
% CC BY-NC-SA 4.0 (http://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

\documentclass[11pt, a4paper, oneside]{Thesis}

\graphicspath{{Figures/}}
\usepackage{float}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{longtable}
\usepackage[backend=bibtex]{biblatex}
\bibliography{Bibliography.bib}

\title{\ttitle}

\begin{document}

\frontmatter

\setstretch{1.3}

\fancyhead{}
\rhead{\thepage}
\lhead{}

\pagestyle{fancy}

\input{variables}

%-------------------------------------------------------------------------------
%   NON-CONTENT PAGES
%-------------------------------------------------------------------------------
\maketitle
\Declaration
\Certificate

\begin{abstract}
We present a transparent, nine-factor investment index that integrates environmental, social and governance (ESG) indicators with financial and operational metrics in a single, reproducible framework. The model is evaluated on 276 mid-cap companies (186~US, 90~India) across 11 GICS sectors, and we place all factor scores on a common 0--100 scale using variable-type-aware normalisation and consensus-based outlier detection. Because ESG measurement still relies on proxy scores derived from 12 financial observables with sector-imputed fallbacks, we interpret the apparent ESG--financial fit ($R^2 = 0.544$) as a proxy artefact rather than independent empirical evidence. We therefore treat the framework primarily as a disciplined stock-selection and portfolio-characterisation tool. Cross-provider validation against MSCI, S\&P~Global, and Sustainalytics ($N{=}10$) remains consistent with the ESG rating divergence documented in the literature. At the same time, a maximum VIF of 2.80 and three principal components explaining 67.4\% of variance indicate limited multicollinearity in the revised factor structure. In portfolio testing, the Balanced strategy shows strong defensive behaviour, with bear-market excess return of $+7.27\%$, rolling excess performance of $+7.38\%$, and bear-period excess of $+10.65\%$ in the updated benchmark summary. Robustness checks also improve: ranking stability reaches Kendall $\tau = 1.000$, cross-validation reports an overfit ratio of 0.499, and factor ablation shows that \texttt{growth\_score} is now the most influential component for rank disruption ($\tau = 0.777$). Profile differentiation remains meaningful but incomplete, as ESG-First and Financial-First record Kendall $\tau = 0.593$ with 7 of the top 10 holdings overlapping. Quintile analysis continues to produce large effect sizes, with Cohen's $d$ up to 2.781 for financial score and 1.906 for ESG composite separation. Overall, we find that the multi-factor approach yields differentiated, defensible portfolios, but the scoring architecture is more reliable than the current return-optimisation layer.
\end{abstract}

\begin{acknowledgements}
I would like to sincerely thank my supervisor, Mr.\ Nandan Mishra, for his guidance on index construction and the practical side of quantitative portfolio design. I am equally grateful to my co-supervisor, Dr.\ Dushyant Kumar, for his detailed feedback on the econometric methodology and for keeping me honest about the statistical assumptions. Thanks are also due to the open-source community behind pandas, NumPy, scikit-learn, statsmodels, and matplotlib---tools without which this work would not have been possible. Any errors that remain are, of course, entirely my own.
\end{acknowledgements}

%-------------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES PAGES
%-------------------------------------------------------------------------------

\pagestyle{fancy}

\tableofcontents

\listoffigures

\listoftables

%-------------------------------------------------------------------------------
%	ABBREVIATIONS
%-------------------------------------------------------------------------------

\clearpage

\setstretch{1.5}

\listofsymbols{ll}
{
	\textbf{ESG}    & Environmental, Social and Governance \\
	\textbf{AUM}    & Assets Under Management \\
	\textbf{PCA}    & Principal Component Analysis \\
	\textbf{VIF}    & Variance Inflation Factor \\
	\textbf{HHI}    & Herfindahl--Hirschman Index \\
	\textbf{ROA}    & Return on Assets \\
	\textbf{ROE}    & Return on Equity \\
	\textbf{MAD}    & Median Absolute Deviation \\
	\textbf{OLS}    & Ordinary Least Squares \\
	\textbf{GICS}   & Global Industry Classification Standard \\
	\textbf{XBRL}   & eXtensible Business Reporting Language \\
	\textbf{ANOVA}  & Analysis of Variance \\
	\textbf{IQR}    & Interquartile Range \\
}

\clearpage

%-------------------------------------------------------------------------------
%	THESIS CONTENT - CHAPTERS
%-------------------------------------------------------------------------------

\mainmatter

\pagestyle{fancy}

\input{Chapters/Introduction}
\input{Chapters/Literature_Review}
\input{Chapters/Data_and_Methods}
\input{Chapters/Results}
\input{Chapters/FutureWork}

%-------------------------------------------------------------------------------
%	THESIS CONTENT - APPENDICES
%-------------------------------------------------------------------------------

\addtocontents{toc}{\vspace{2em}}

\appendix

\input{Appendices/AppendixA}
\input{Appendices/AppendixB}
\input{Appendices/AppendixC_ProfileJustification}

\addtocontents{toc}{\vspace{2em}}

\backmatter

%-------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%-------------------------------------------------------------------------------

\label{Bibliography}

\lhead{\emph{Bibliography}}

\printbibliography

\end{document}
